Exploring Bounds

### 2015-04-09 draft.tex
more notes

HELLO!

%First explore linear programming bound
Krawtouck polynomials

>>>>

\section{Introduction}

An interesting problem in coding theory is how to determine the maximum possible
number of codewords in a code.  For an $n$-dimensional code, we are interested in 
the maximum number of codewords such that the code has weight $d$.  
Formally, we use the notation $A_q(n,d)$
and $B_q(n,d)$, defined as the maximum of number of codewords in a code over
$\mathbb{F}_q$ of length $n$ and minimum distance $d$ for an arbitrary (linear
on non-linear) code and linear code, respectively.  It is not always possible to In lecture, we have
considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
lower bounds---Gilbert and Varshamov---on these values.  The purpose of this
paper is to consider other well-known bounds in the literature.

This paper is broken up into $x$ sections.

%First explore linear programming bound
Asymptotic singleton, include 2 examples
Asymptotic plotkin, some examples
draw graph
Asymptotic hamming
	define hilbert, prove 135,136, define vq(n,a),
	black box 2.10.3, prove 2.10.5

Table of common$a_q(n,d)$ values
Recall basic theory: thm 2.1.2, 2.1.6

Sections

Plotkin
talk about importance
define it
prove it
work out some examples

Elias
talk about importance
define it
prove two lemmas that do the heavy lifting
easy proof to finish it off
work out some examples

Linear Programming Bound
talk about importance
define it
prove it
work out some examples

Note existence of two lower bounds, say we talked about them in class
